\chapter*{Acknowledgments}
\thispagestyle{empty}
At this point I want to thank the people that support me with this thesis and over the course of my studies.
\\\\
I would like to thank Prof. Dr. Zhe Wang for giving me the opportunity to write a bachelor thesis in his group about such an interesting topic.
It was a very pleasant working environment and I enjoyed coming to the university every day.
\\
In addition, I would like to thank Prof. Dr. Mirko Cinchetti for taking the time to do the Zweitkorrektur of my thesis.
\\\\
Furthermore, I would like to thank my supervisor Patrick for taking so much time to help me with my thesis.
I am grateful that I had such a nice supervisor, that would always try to help me as well as possible.
I enjoyed not only working with him but also the time in between lab sessions.
\\\\
A big thank you also goes to Anneke who helped me a lot with various topics while finalizing my thesis and even took the time to read my thesis in her off time on the weekend.
It was a pleasure spending time with you in the office and having the opportunity to talk to someone when I needed a minute to clear my head.
\\\\
I also want to thank Changqing, who was a very good teacher for all the practical lab work, especially when Patrick was not around.
\\\\
Moreover, I want to thank Frank for his support as the workgroup technician.
%Zhe, Patrick, Anneke, Family, Friends, 
Finally, I would like to thank my friends and family for their support over the whole course of my bachelor thesis.
\clearpage