\begin{thebibliography}{Barkhuijsen, 198585}
\label{literatur}

\bibitem[Aleksandrov, 1979]{aleksandrov} E.B. Aleksandrov, N.I. Kaliteevski,
M.P. Chaika, Sov. Phys. Usp. \bf 22\rm, 760 (1979).

\bibitem[Balslev, 1982]{balslev} I. Balslev, A. Stahl, Phys. Stat. Sol. (B) 
\bf 111\rm, 531 (1982).

\bibitem[Barkhuijsen, 1985]{bark} H. Barkhuijsen, R. de Beer, W.M.M.J. BovÇe
and D. van Ormondt, Journal Of Magnetic Resonance \bf 61\rm , 465--481 (1985).

\bibitem[Bassani, 1985]{bassani} F. Bassani und L.C. Andreoni, in \it Proceedings
of the International School of Physics 'Enrico Fermi'\rm, Course 96, Hrsg. U.M.
Grassano und N. Terzi, Varenna, Italy (1985).

\bibitem[Battaglia, 1984]{battaglia} G. Battaglia, A. Quattropani und P. Schwendimann,
Solid State Communication \bf 49\rm, 985 (1984).

\bibitem[Bed.Anl.Antares]{antares} \it Operator's Manual Antares 76--S YLF\rm,
Coherent Inc., Palo Alto, USA.

\bibitem[Bir, 1973]{bir} G.L. Bir und G.E. Pikus, Sov. Phys. JETP \bf 37\rm,
1116 (1973).

\bibitem[Blum, 1981]{blum} K. Blum, \it Density Matrix Theory and Applications\rm, Plenum Press,
New York (1981).

\bibitem[Bonnot, 1974]{bonnot}A. Bonnot, R. Planel, C. BÇnoit Ö la Guillaume,
Phys. Rev. B \bf 9\rm, 690 (1974). 

\bibitem[Brigham, 1985]{brigham} E. Oran Brigham, \it FFT Schnelle Fourier--Transformation\rm,
R. Oldenbourg Verlag, MÅnchen, Wien (1985).

\bibitem[Broser, 1980]{broser} I. Broser, M. Rosenzweig, Solid State Commun.
\bf 36\rm, 1027 (1980).

\bibitem[Demtrîder, 1993]{demtroeder} W. Demtrîder, \it Laser Spectroscopy\rm, 
Springer--Verlag, Berlin, Heidelberg, New York (1993).

\bibitem[Dietze, 1994]{dietze} C. Dietze, Hauptpraktikum, Paderborn (1994).

\bibitem[Feynman, 1965]{feynman} R.P. Feynman, R.B. Leighton, M. Sands, \it The
Feynman lectures on physics\rm, Addison--Wesley (1965).

\bibitem[Fick, 1968]{fick} E. Fick, \it EinfÅhrung in die Grundlagen der Quantentheorie\rm,
Aula--Verlag, Wiesbaden (1968).

\bibitem[Gornik, 1972]{gornik} W. Gornik, D. Kaiser, W. Lange, J. Luther, H.H. Schulz,
Opt. Commun. \bf 6\rm, 327, (1972).

\bibitem[Gross, 1964]{gross}E.F. Gross, S.A. Permogorov, B.S. Razbirin, 
Sov. Phys. -- Doklady \bf 9\rm, 164 (1964).

\bibitem[Haroche, 1976]{haroche} S. Haroche, in \it High Resolution Spectroscopy\rm,
Hrsg. K. Shimoda, Springer--Verlag, Berlin, Heidelberg (1976). 

\bibitem[Haynes, 1960]{haynes} J.R. Haynes, Phys. Rev. Lett. \bf 4\rm, 361 (1960).

\bibitem[Hellwege, 1988]{hellwege} K.-H. Hellwege, \it EinfÅhrung in die Festkîrperphysik\rm,
Springer--Verlag, Berlin, Heidelberg (1988).

\bibitem[Henry, 1970]{henry} C.H. Henry, K. Nassau, Phys. Rev. B, \bf 1\rm, 1628 (1970). 

\bibitem[Hopfield, 1958]{hopfield58} J.J. Hopfield, Phys. Rev. \bf 112\rm, 1555 (1958).

\bibitem[Jackson, 1983]{jackson} J.D. Jackson, \it Klassische Elektrodynamik\rm,
2. Aufl., Walter de Gruyter, Berlin (1983).

\bibitem[JÅtte, 1992]{juette1} M. JÅtte, Diplomarbeit, Paderborn (1992).

\bibitem[JÅtte, 1995]{juette2} M. JÅtte, private Mitteilungen, Paderborn (1995).

\bibitem[Kay, 1981]{kay} S.M. Kay, S.L. Marple, Proc. IEEE \bf 69\rm , 1380 (1981).

\bibitem[Kiene, 1992]{kiene} M. Kiene, Diplomarbeit, Paderborn (1992).

\bibitem[Koster, 1963]{koster} G.G. Koster, J.O. Dimmock, R.G. Wheeler, H. Statz,
\it Properties of the thirty--two point groups\rm, M.I.T. Press, Cambridge Massachusetts
(1963). 

\bibitem[Kumaresan, 1982]{kumaresan} R. Kumaresan and D.W. Tufts, IEEE Trans.
\bf ASSP--30\rm, 833 (1982).

\bibitem[Landolt, 1983]{landolt} Landolt--Bîrnstein, Vol. \bf 17b\rm , 
Springer--Verlag, Berlin, Heidelberg, New York (1983).

\bibitem[Langer, 1990]{langer2} V. Langer, H. Stolz und W. von der Osten,
Phys. Rev. Lett. \bf 64\rm, 854 (1990).

\bibitem[Langer, 1992]{langer} V. Langer, Dissertation, Paderborn (1992).

\bibitem[Lawson, 1974]{lawson} C.L. Lawson and R.J. Hanson, \it Solving Least 
Squares Problems\rm, Prentice--Hall, Englewood Cliffs, N.J., 1974.

\bibitem[Makhoul, 1978]{makhoul} J. Makhoul, in \it Modern Spectral Analysis \rm 
(D. G. Childers Ed.), pp. 99--118, IEEE Press, Wiley, New York, 1978.

\bibitem[MÅller, 1994]{muller} U. MÅller, Hauptpraktikum, Paderborn (1994).

\bibitem[Perlow, 1978]{perlow} G. J. Perlow, Phys. Rev. Lett. \bf 40\rm, 896 (1978).

\bibitem[Permogorov, 1995]{permogorov} S. Permogorov, private Mitteilungen, Paderborn (1995).

\bibitem[Pikus, 1982]{pikus} G.E. Pikus, E.L. Ivchenko, in \it Excitons\rm,
edited by E.I. Rashba, M.D. Sturge, North--Holland Publ. Comp., Amsterdam (1982).

\bibitem[Rashba, 1962]{rashba1} E.I. Rashba, G.E. Gurgenishvili, 
Soviet Phys. -- Solid State \bf 4\rm, 759 (1962).

\bibitem[Rashba, 1982]{rashba} E.I. Rashba, M.D. Sturge, \it Excitons\rm, 
North--Holland Publ. Comp., Amsterdam (1982).

\bibitem[Rooymans, 1963]{rooymans} C. J. M. Rooymans, Phys. Lett. \bf 4\rm, 186 (1963).

\bibitem[Schicht, 1994]{schicht} B. Schicht, Diplomarbeit, Paderborn (1994).

\bibitem[Schreiber, 1989]{schreiber} E. Schreiber, Dissertation, Paderborn (1989).

\bibitem[Skettrup, 1971]{skettrup} T. Skettrup, M. Suffczynski, W. Gorzkowski,
Phys. Rev. B, \bf 4\rm, 512 (1971).

\bibitem[Stauffer, 1983]{stauffer} L. Stauffer, B. StÇbÇ, G. Munschy,
Stat. Sol. (b), \bf 119\rm, 193 (1983).

\bibitem[StÇbÇ, 1983]{stebe} B. StÇbÇ, F. Dujardin, G. Munschy, \it Int. Conf. on
the Application of High Magnetic Fields in Semiconductor Physics\rm, Grenoble 1982,
Ed. G. Landwehr, Springer--Verlag, Berlin (1983).

\bibitem[Stenholm, 1984]{stenholm} S. Stenholm, \it Foundations of Laser Spectroscopy\rm,
John Wiley \& Sons Inc., New York (1984).

\bibitem[Stolz, 1991]{stolz1} H. Stolz, V. Langer, E. Schreiber, S. Permogorov,
W. von der Osten, Phys. Rev. Lett. \bf 67\rm, 679 (1991).

\bibitem[Stolz, 1993]{stolz} H. Stolz, Habilitation, Paderborn (1993).

\bibitem[Stolz, 1995]{stolz3} H. Stolz, private Mitteilungen, Paderborn (1995).

\bibitem[Thomas, 1961]{thomas61} D.G. Thomas und J.J. Hopfield, Phys. Rev. Lett.
\bf 7\rm, 316 (1961).

\bibitem[Thomas, 1962]{thomas62} D.G. Thomas und J.J. Hopfield, Phys. Rev. 
\bf 128\rm, 2135 (1962).

\bibitem[Weber, 1989]{weber89} Th. Weber, Diplomarbeit, Paderborn (1989).
\addcontentsline{toc}{chapter}{Literaturverzeichnis}

\bibitem[Weiss, 1983]{weiss} A. Weiss, H. Witte, \it Kristallstruktur und
chemische Bindung\rm, Verlag Chemie, Weinheim (1983).

\end{thebibliography}

