\begin{thebibliography}{giese-bogdan,199797}
\label{literatur}
\addcontentsline{toc}{chapter}{Literaturverzeichnis}

%\bibitem[Bauer, 1991]{bauer91}Bauer, G., Wegscheider, W., Ortner, H.M.,
%\it Selectivity and error estimating in multivariate calibration
%applicating to segmented ICP-OES\rm , Spectrochim. Acta 46 \bf
%B\rm , 1185 (1991).

\bibitem[Becker--Ross, 1997]{becker-ross97} Becker--Ross, H.,
Florek, S.V., \it Echelle spectrometers and
charge--coupled--devices\rm , Spectrochim. Acta B, \bf 52\rm ,
1367--1375, (1997).

\bibitem[BMBF, 1999]{bmbf99} Bernhofer, C., Crutzen, P., Fischer,
H. Heintzenberg, J., Lemke, P. Zellner, R., \it Konzept f\"{u}r
vorrangige mittelfristige deutsche Atmosph\"{a}renforschung\rm ,
Bundesministerium f\"{u}r Bildung und Forschung, Berlin, (auch im
Internet verf\"{u}gbar: www.gsf.de/ptukf/afo\_2000), (1999).

%\bibitem[Berry, 1998]{berry98} Berry, R.J., and Griffiths, P.R.,
%\it Genetic algorithms for spectral window selection in open--path
%Fourier transform infrared spectrometry\rm , Fourier Transform
%Spectroscopy, 11th Intern. Conference, J.A. de Haseth, Hrsg., AIP
%Conference Proc. \bf 430\rm , Am. Institute of Physics, New York,
%237--240, (1998).

\bibitem[Brown, 1996]{brown96} Brown, L.R., Gunson, M.R., Toth,
R.A., Irion, F.W., Rinsland, C.P., Goldman, A., \it 1995
Atmospheric Molecule Spectroscopy (ATMOS) Linelist\rm , Appl.
Optics \bf 35\rm , 16, 2828--2848, (1996).

\bibitem[Cameron, 1982]{cameron82} Cameron, D.G., Kauppinen, J.K.,
Moffatt, D.J., Mantsch, H.H., \it Precision in Condensed Phase
Vibrational Spectroscopy\rm , Appl. Spectrosc. \bf 36\rm ,
245--250, (1982).

\bibitem[Caspary, 1998]{caspary98}Caspary, H.J., \it
Hochwasserversch\"{a}rfung infolge von Klima\"{a}nderungen\rm, GEO,
Hamburg, 259, (1998).

\bibitem[Chaffin, 1999]{chaffin99} Chaffin, C.T. Jr., Marshall,
T.L., Chaffin, N.C., \it Passive FTIR Remote Sensing of Smokestack
Emissions\rm , Field Analytical Chemistry and Technology \bf 3\rm
(2), 111--115, (1999).\\

\bibitem[Chase, 1982]{chase82}Chase, D.B., \it Phase Correction in
FT--IR\rm, Appl. Spectrosc. \bf 36\rm, 240--244, (1982).

\bibitem[Chu, 1998]{chu98} Chu, P.M., Rhoderick, G.C., Van Vlack,
D., Wetzel, S.J., Lafferty, W.J., Guenther, F.R., \it A
quantitative infrared spectral database of hazardous air
pollutants\rm , Fresenius J. Anal. Chem., \bf 360\rm , 426-429,
(1998).

\bibitem[Clerbaux, 1995]{clerbaux95} Clerbaux, C., Chazette, P.,
Megie, G., \it Tropospheric concentrations of infrared absorbing
molecules using a nadir--looking Fourier transform
spectrometer\rm, Proc. SPIE--int. Soc. Opt. Eng. \bf 2578\rm,
148-153, (1995).

\bibitem[Cuhls, 1998]{cuhls98} Cuhls, C., Doedens, H., \it
Emissions from mechanical and biological treatment plants\rm ,
Konferenzbericht DepoTech Abfallwirtschaftstag, 4th, D. Hengerer,
Hrsg., Publisher, Balkema, Rotterdam, Neth., 33-47, (1998).

\bibitem[Demtr\"{o}der, 1993]{demtr\"{o}der93} Demtr\"{o}der, W.,
Laserspektroskopie--Grundlagen und Techniken, 3. Auflage,
Springer, Berlin, (1993).

\bibitem[DFG, 1999]{dfg99} Deutsche Forschungsgemeinschaft, MAK--
und BAT--Werte--Liste 1999, Wiley, VCH, Weinheim, (1999).

\bibitem[Ehrentreich, 1997]{ehrentreich97} Ehrentreich, F.,
\it Derivation of substructures from infrared band shapes by fuzzy
logic and partial cross correlation functions\rm , Fresenius' J.
Anal. Chem. \bf 359(1)\rm , 56-60, (1997).

\bibitem[Espinoza, 1998]{espinoza98} Espinoza, L.H., Niemczyk,
T.M., Stallard, B.R., \it Generation of Synthetic Background
Spectra by Filtering the Sample Interferogram in FT-IR\rm , Appl.
Spectrosc. \bf 52\rm , 375-379, (1998).

\bibitem[Farmer, 1997]{farmer97}Farmer, C.B., \it Stratospheric
FTS\rm , Mikrochim Acta \bf 14\rm , 89--101, (1997).

\bibitem[Gasteiger, 1997]{gasteiger97} Gasteiger, J., Schuur, J.,
Selzer, P., Steinhauer, L., Steinhauer, V., \it Finding the 3D
structure of a molecule in its IR spectrum\rm , Fresenius' J.
Anal. Chem. \bf 359(1)\rm , 50-55, (1997).

\bibitem[Giese-Bogdan, 1997]{giese97} Giese-Bogdan, S., Levine,
S.P., Molt, K., \it Methods of Background Correction in the open
path Fourier transform infrared spectroscopy - The shifting method
as a new tool\rm , Proc. SPIE \bf 3106\rm , 199-209, (1997).

\bibitem[Golub, 1989]{golub89} Golub, B.H. und van Loan, C.F.,
Matrix Computations, 2. Auflage, John Hopkins University,
Baltimore, (1989).

\bibitem[Gottwald, 1997]{gottwald97} Gottwald, W., Wachter, G.,
\it IR--Spektroskopie f\"{u}r Anwender\rm , Hrsg. Gruber, U., Klein,
W., Wiley--VCH, Weinheim, (1997).

\bibitem[Griffith, 1996]{griffith96} Griffith, D.W.T., \it Synthetic
calibration and quantitative analysis of gas-phase FT-IR
spectra\rm , Appl. Spectrosc. \bf 50\rm , 59-70, (1996).

\bibitem[Griffiths, 1977]{griffiths77} Griffiths, P.R., Sloane,
J., Hannah, R.W., \it Interferometers vs Monochromators:
Separating the Optical and Digital Advantages\rm , Appl.
Spectroscopy \bf 31\rm , 485--495, (1977).

\bibitem[Griffiths, 1986]{griffiths86} Griffiths, P.R., de Haseth, J.A.,
\it Fourier Transform Infrared Spectrometry\rm , John Wiley \&
Sons, New York, (1986).

\bibitem[Griffiths, 1994]{griffiths94} Griffiths, P.R., \it FT--IR
spectrometry at low resolution: How low can you go?\rm , Proc.
SPIE \bf 2089\rm , 2-8, (1994).

\bibitem[Grisar, 1992]{grisar92} Editors Grisar, R., B\"{o}ttner, H., Tacke,
M., Restelli, G., Monitoring of Gaseous Pollutants by Tunable
Diode Lasers, Proceedings of the International Symposium held in
Freiburg, Germany, October 1991, Kluwer Academic Publishers,
Dordrecht, (1992).

\bibitem[Gu, 1998]{gu98} Gu, B., Wang, J., Zhou, X., Wu, X., Liu, F., Li, Y.,
\it Comparison of multivariate calibration methods for
quantitative analysis of multicomponent mixture of air toxic
organic compounds by FTIR\rm , J. Environ. Sci. Health \bf A33\rm
, 1419-1436, (1998).

\bibitem[G\"{u}nzler, 1996]{g\"{u}nzler96} G\"{u}nzler, H., Heise, H.M., IR--Spektroskopie,
eine Einf\"{u}hrung\rm , VCH, Weinheim, (1996).

%\bibitem[Gunst, 1980]{gunst80} Gunst, R.F. und Mason, R.L., Regression
%Analysis and its Application, Marcel Dekker, New York, (1980).

\bibitem[Haaland, 1980]{haaland80} Haaland, D.M. and Easterling, R.G.,
\it Improved sensitivity of infrared spectroscopy by the
application of least squares methods\rm , Appl. Spectrosc. \bf
34\rm , 539-548, (1980).

\bibitem[Haaland, 1985]{haaland85} Haaland, D.M., \it Theoretical Comparison
of Classical and Inverse Least--Squares Methods for Quantitative
Infrared Spectroscopy\rm , 1985 International Conference on
Fourier and Computerized Infrared Spectroscopy, J.G. Grasseli,
D.G. Cameron, Hrsg., Proc. SPIE \bf 553\rm , 241-242, (1985).

\bibitem[Haaland, 1987]{haaland87} Haaland, D.M., \it Methods to include Beer's
law nonlinearities in quantitative spectral analysis\rm ,
Computerized Quantitative Analysis, ASTM STP \bf 934\rm , G.L.
McClure, Hrsg., American Society for Testing and Materials,
Philadelphia, 78-94, (1987).

\bibitem[Haaland, 1988]{haaland88} Haaland, D.M., Thomas, E.V.,
\it Parital Least--Squares Methods for Spectral Analyses. 1.
Relation to Other Quantitative Calibration Methods and the
Extraction of Qualitative Information\rm , Anal. Chem. \bf 60\rm,
1193-1202, (1988).

\bibitem[Hanst, 1994]{hanst94} Hanst, P.L., Hanst, S.T., \it Gas
measurements in the fundamental infrared region\rm , in: Air
monitoring by spectroscopic techniques, Hrsg. M.W. Sigrist, John
Wiley \& Sons, New York, 335-470, (1994).


\bibitem[Hanst, 1997]{hanst97} Hanst, P.L., Hanst, S.T, Williams,
G.M., \it Infrared Spectra for Quantitative Analysis of Gases\rm ,
Handbuch zur IR-Spektrendatenbank, Infrared Analysis Inc.,
Anaheim, CA 92801, (1998).

%\bibitem[Hart, 1998]{hart98} Hart B.K., Griffiths, P.R., \it Use
%of partial least squares regression for the multivariate
%calibration of hazardous air pollutants in open--path FT--IR
%spectrometry\rm, Fourier Transform Spectroscopy, 11th Intern.
%Conference, J.A. de Haseth, Hrsg., AIP Conference Proc. \bf
%430\rm, Am. Institute of Physics, New York, 241-244, (1998).

\bibitem[Hartmann, 1988]{hartmann88} Hartmann, J.M., Rosenmann,
L., Perrin, M.Y., Taine, J. \it Accurate calculated tabulations of
CO line broadening by H\down{2}O, N\down{2}, O\down{2}, and
CO\down{2} in the 200--3000--K temperature range\rm , Applied
Optics \bf 27\rm (15), 3063--3065, (1988).

\bibitem[Heise, 1985]{heise85} Heise, H.M., Kirchner, H.-H.,
Richter, W., \it Calibration Method for the
Infrared--Spectrometric Trace Gas Analysis\rm , Fresenius' Z Anal.
Chem. \bf 322\rm , 397-400, (1985).

\bibitem[Heise, 1996]{heise96} Heise H.M., Infrarotspektrometrische
Gasanalytik -- Verfahren und Anwendungen in der
Infrarotspektroskopie, Hrsg. H. G\"{u}nzler et al., 1-101, Springer,
Berlin, (1996).

%\bibitem[Heise, 1997]{heise97} Heise, H.M. and Bittner, A., \it Rapid
%and Reliable Spectral Variable Selection for Statistical
%Calibrations based on PLS--Regression Vector Choices", Fresenius'
%J. Anal. Chem. \bf 359\rm , 93-99, (1997).

\bibitem[Henrion, 1995]{henrion95} Henrion, R., Henrion, G.,
Multivariate Datenanalyse, Springer, Berlin, (1995).

\bibitem[Higham, 1996]{higham96} Higham, N.J., Accuracy and
Stability of Numerical Algorithms, SIAM, Philadelphia, (1996).

\bibitem[Hirschberger, i.p.]{hirschbergerip} Hirschberger, R.,
\it Automotive Emissions Analysis with Spectroscopic Techniques\rm
, in Encyclopedia of Analytical Chemistry: Instrumentation and
Applications, editor--in--chief Meyers, R.A., John Wiley \& Sons,
New York, (in press).

\bibitem[Hollas, 1992]{hollas92} Hollas, J.M., Modern
Spectroscopy -- 2nd Edition, John Wiley \& Sons, Chichester,
(1992).

\bibitem[Husson, 1993]{husson93} Husson, N., Chedin, A., Bonnet,
B., \it Review Of Existing Spectral Line Data Catalogs\rm , in
High Spectral Resolution Infrared Remote Sensing for Earth's
Weather and Climate Studies, Hrsg. Chedin, A., Chahine, M.T.,
Scott, N.A., Springer, Berlin, (1993).

\bibitem[Husson, 1999]{husson99} Jacquinet--Husson, N., Arie, E.,
Ballard, J., Barbe, A. et al., \it The 1997 spectroscopic GEISA
database\rm, J. Quant. Spectrosc. Radiat. Transfer \bf 62(3)\rm,
205--254, (1999).

\bibitem[Jaakola, 1997]{jaakola97} Jaakkola, P., Tate, J.D., Paakkunainen,
M., Kauppinen, J., Saarinen, P., \it Instrumental resolution
considerations for Fourier Transform Infrared Gas-Phase
spectroscopy\rm , Appl. Spectrosc. \bf 51\rm , 1159-1169, (1997).

\bibitem[Johansen, 1997]{johansen97}Johansen, I.-R., Lines, G.T., Honne, A.,
Midtgaard, T., \it Calibration of an FT--IR spectrometer for
ambient air monitoring using PLS\rm , Appl. Spectrosc. \bf 51\rm ,
1540-1546, (1997).

\bibitem[Keens, 1990]{keens90} Keens, A., Simon, A.
US patent No. 4, 927, 269 (22 May 1990).

\bibitem[Keens, 1993]{keens93} Keens, A., Simon, A.,
\it Correction for the non--linear response of infrared
detectors\rm , 9th Int. Conf. Fourier Transform Spectrosc., ed. by
J.E. Bertie und H. Wieser, Proceedings of SPIE \bf 2089\rm ,
222-223, (1993).

\bibitem[Kroutil, 1994]{kroutil94} Kroutil, R.T., Combs, R.J., Knapp, R.B., Small, G.W.,
\it Automated Detection of Acetone, Methyl Ethyl Ketone, and
Sulfur Hexafluoride by Direct Analysis of Fourier Transform
Infrared Interferograms\rm , Appl. Spectr. \bf 48\rm , 724-732,
(1994).

\bibitem[Kyle, 1984]{kyle84} Kyle, T.G., Blatherwick, R., \it
Smearing of interferograms in Fourier transform spectroscopy\rm ,
Applied Optics \bf 23\rm (2), 261--263, (1984).

\bibitem[Lowry, 1985]{lowry85} Lowry, S.R., Huppler, D.A., Anderson, C.R.,
\it Data base development and search algorithms for automated
infrared spectral identification\rm , J. Chem. Inf. Comput. Sci.
\bf 25\rm , 235-241, (1985).

%\bibitem[Marbach, 1990]{marbach90} Marbach, R., Heise, H.M., \it Calibration
%Modeling by Partial Least--Squares and Principal Component
%Regression and its Optimization Using an Improved Leverage
%Correction for Predection Testing\rm , Chemometrics and Int. Lab.
%Systems \bf 9\rm , 45-63, (1990).

%\bibitem[Marbach, 1992]{marbach92} Marbach, R., Heise, H.M., \it On the efficiency
%of algorithms for multivariate linear calibration used in
%analytical spectroscopy\rm , Trends in Anal. Chem. \bf 11\rm ,
%270-275, (1992).

\bibitem[Martens, 1991]{martens91} Martens, H. und Naes, T., Multivariate Calibration,
2. Auflage, John Wiley, Chichester, (1991).

\bibitem[Massart, 1988]{massart88} Massart, D.L., Vandeginste,
B.G.M., Demin, S.N., Michotte, Y., Kaufman, L., Chemometrics, a
textbook, Elsevier, Amsterdam, (1988).

\bibitem[Mattu, i.p.]{mattuip} Mattu, M.J., Small G.W., \it
Quantitative Analysis of Sulfur Dioxide with Passive Fourier
Transform Infrared Remote Sensing Interferogram Data\rm , Appl.,
Spectroscopy, (in press).

\bibitem[Measures, 1984]{measures84} Measures, R.M., Laser Remote
Sensing, Fundamentals and Applications, J. Wiley \& Sons, New
York, (1984).

\bibitem[Mertz, 1967]{mertz67} Mertz, L., \it Auxiliary Computation For Fourier
Spectrometry\rm , Infrared Phys. \bf 7\rm , 17--23, (1967).

\bibitem[Phillips, 1996]{phillips96} Phillips, A.J., Hamilton, P.A., \it Improved Detection
Limits in Fourier Transform Spectroscopy from a Maximum Entropy
Approach to Baseline Estimation\rm , Anal. Chem. \bf 68\rm ,
4020-4025, (1996).

\bibitem[Platt, 1994]{platt94} Platt, U., \it Differential Optical Absorption
Spectroscopy (DOAS)\rm , in: Air monitoring by spectroscopic
techniques, Hrsg. M.W. Sigrist, John Wiley \& Sons, New York,
335-470, (1994).

%\bibitem[Rothman, 1992]{rothman92} Rothman, L.S., Gamache, R.R. et al.,
%\it The Hitran Molecular Database, Editions of 1991 and 1992\rm ,
%J. Quant. Spectrosc. Radiat. Transfer \bf 48\rm , 469-507, (1992).

\bibitem[Ramsay, 1952]{ramsay52} Ramsay, D.A., \it Intensities and
Shapes of Infrared Absorption Bands of Substances in the Liquid
Phase\rm , J. Am. Chem. Soc. \bf 74\rm , 72--80, (1952).

\bibitem[Richardson1, 1998]{richardson198} Richardson, R.L. Jr., Yang, H., Griffiths, P.R.,
\it Evaluation of a correction for photometric errors in FT--IR
spectrometry introduced by a nonlinear detector response\rm ,
Appl. Spectr. \bf 52\rm , 572-578, (1998).

\bibitem[Richardson2, 1998]{richardson298}Richardson, R.L.,
Griffiths, P.R., \it Reduction of Stray Light in Monostatic
Open--Path FT--IR Spectrometers with a Plane Correction Mirror\rm,
Appl. Spectr. \bf 51\rm , 1254--1256, (1998).

\bibitem[Rothman, 1998]{rothman98} Rothman, L.S., Rinsland, C.P.,
Goldman, A., Massie, S.T., Edwards, D.P., Flaud, J.--M., Perrin,
A., Camy--Peyret, C., Dana, V., Mandin, J.--Y., Schroeder, J.,
Mccann, A., Gamache, R.R., Wattson, R.B., Yoshino, K., Chance,
K.V., Jucks, K.W., Brown, L.R., Nemtchinov, V., Varanasi, P., \it
The HITRAN Molecular Spectroscopic Database and HAWKS (HITRAN
Atmospheric Workstation): 1996 Edition\rm, J. Quant. Spectrosc.
Radiat. Transfer \bf 60(5)\rm, 665--710, (1998).

\bibitem[Rutan, 1984]{rutan84} Rutan, S.C,, Brown, S.D., \it
Adaptive Kalman Filtering Used To Compensate For Model Errors In
Multicomponent Methods\rm , Analytica Chimica Acta \bf 160\rm ,
99-119, (1984).

\bibitem[Saarinen, 1991]{saarinen91} Saarinen, P., Kauppinen, J,
\it Multicomponent Analysis of FT--IR Spectra\rm , J. Appl.
Spectrosc. \bf 45\rm , 953-963, (1991).

\bibitem[Sch\"{a}fer, 1995]{schaefer95} Sch\"{a}fer, K., Haus, R., Heland, J., Haak, A.,
\it Measurements of atmospheric trace gases by emission and
absorption spectroscopy with FTIR\rm , Ber. Bunsenges. Phys. Chem.
\bf 99\rm , 405-411, (1995).

\bibitem[Sch\"{o}nwiese, 1999]{schoenwiese99} Sch\"{o}nwiese, C. D., \it
Das Klima der j\"{u}ngeren Vergangenheit\rm , Physik in unserer Zeit,
\bf 3/99\rm , 94--101, (1999).

\bibitem[Schrader, 1995]{schrader95} Hrsg. Schrader, B., Infrared and
Raman Spectroscopy, VCH, Weinheim, (1995).

\bibitem[Seinfeld, 1998]{seinfeld98} Seinfeld, J.H., Pandis, S.N.,
Atmospheric Chemistry and Physics, John Wiley \& Sons, New York,
(1998).

\bibitem[Silver, 1992]{silver92} Silver, J.A., \it
Frequency--modulation spectroscopy for trace species detection:
theory and comparison among experimental methods\rm , Applied
Optics \bf 31 \rm (6), 707--717, (1992).

\bibitem[TO--16, 1997]{to1697} Compendium of
Methods for the Determination of Toxic Organic Compounds in
Ambient Air, 2nd. ed., Compendium Method TO--16:\it Long--Path
Open--Path Fourier Transform Infrared Monitoring of Atmospheric
Gases\rm , Center for Environmental Research Information, Office
of Research and Development, U.S. Environmental Protection Agency,
Cincinatti, OH 45268, (January 1997).

%\bibitem[Tranter, 1990]{tranter90} Tranter, R.L., \it The Kalman Filter -- An Alternative
%Approach to Quantitative Analysis\rm , Anal. Proceedings \bf 27\rm
%, 134-136, (1990).

\bibitem[Traub, 1998]{traub98}Traub, W.A., \it Atmospheric FTS\rm
, Fourier Transform Spectroscopy, 11th Intern. Conference, J.A. de
Haseth, Hrsg., AIP Conference Proc. \bf 430\rm , Am. Institute of
Physics, New York, 60--73, (1998).

\bibitem[Turk, 1997]{turk97} Turk, M., Turk, T., Collins, H.J.,
\it Mechanical-biological processes for material--specific waste
processing\rm , Beih. M\"{u}ll Abfall \bf 33\rm , 126-131, (1997).

\bibitem[Van Huffel, 1991]{vanhuffel91} Van Huffel, S.,
Vandewalle, J., The Total Least Squares Problem: Computational
Aspects and Analysis, SIAM, Philadelphia, (1991).

\bibitem[VDI, 1998]{vdi98} VDI 4211 (Blatt 1, Entwurf) Fernmessverfahren -- Messungen
gasf\"{o}rmiger Emissionen und Immissionen -- Grundlagen, Verein
Deutscher Ingenieure, (Jan. 1998).

\bibitem[Werle, 1998]{werle98} Werle, P., \it High sensitivity Gas
Analysis by mid and near Infrared Diode Lasers\rm , proceedings of
the 5th International Symposium on Gas Analysis by Tunable Diode
Lasers, Freiburg 1998, VDI--Berichte \bf 1366\rm , 1--16, (1998).

\bibitem[W\"{u}lbern, 1998]{wuelbern98} W\"{u}lbern, K., \it Measuring air pollutants in presence of
high water vapour concentrations\rm , Fourier Transform
Spectroscopy, 11th Intern. Conference, J.A. de Haseth, Hrsg., AIP
Conference Proc. \bf 430\rm , Am. Institute of Physics, New York,
215-218, (1998).

\bibitem[Xiao, 1993]{xiao93} Xiao, H., Livine, S.P., \it Application of computerized differentiation
technique to remote--sensing Fourier transform infrared
spectrometry for analysis of toxic vapors\rm , Anal. Chem. \bf
65\rm , 2262, (1993).

\bibitem[Yang, 1998]{yang98} Yang, H., Griffiths, P.R.,
\it Application of Neural Networks to Compound Identification in
Open--Path FT--IR Spectrometry\rm , Fourier Transform
Spectroscopy, 11th Intern. Conference, J.A. de Haseth, Hrsg., AIP
Conference Proc. \bf 430\rm , Am. Institute of Physics, New York,
245--248, (1998).

\bibitem[Zellner, 1993]{zellner93} Zellner, R., \it Ozonabbau in
der Stratosph\"{a}re: Ausma{\ss}, Ursachen und Folgen\rm , Vortr\"{a}ge und
Berichte zum Kolloquium 'Drei Jahrzehnte Luftqualit\"{a}ts\"{u}berwachung
-- Bilanz und Perspektiven', Landesanstalt f\"{u}r Imissionsschutz
NRW, 25--34, (1993)
%\bibitem[Zhu, 1994]{zhu94} Zhu, C., Griffiths, P.R., \it Extending the range of Beer's law in
%FT--IR spectrometry by selection of the apodization function\rm ,
%Proc. SPIE \bf 2089\rm , 434-435, (1994).

\bibitem[Zhu1, 1998]{zhu198} Zhu, C., Griffiths, P.R., \it Extending the Range
of Beer's Law in FT--IR Spectrometry. Part I: Theoretical Study of
Norton--Beer Apodization Functions\rm , Appl. Spectr. \bf 52\rm ,
1403--1408, (1998).

\bibitem[Zhu2, 1998]{zhu298} Zhu, C., Griffiths, P.R., \it Extending the Range
of Beer's Law in FT--IR Spectrometry. Part II: Theoretical Study
of Continuous Apodization Functions\rm , Appl. Spectr. \bf 52\rm ,
1409--1413, (1998).

\bibitem[Zybin, 1995]{zybin95}Zybin, A., Schn\"{u}rer--Patschan, C.,
Niemax, K., \it Wavelength Modulation Diode Laser Atomic
Absorption Spectrometry in Modulated Low--pressure Helium Plasmas
for Element--Selective Detection in Gas Chromatography\rm , J.
Anal. At. Spectrom. \bf 10\rm, 563, (1995).

\end{thebibliography}

\cleardoublepage
